Cycle Route Uptake and Scenario Estimation (CRUSE): an approach for developing strategic cycle network planning tools

### 2024-03-24 paper.qmd
Update title

---
title: "Cycle Route Uptake and Scenario Estimation (CRUSE): an open and nationally scalable approach for strategic cycle network planning tool development"
subtitle: A case study of Ireland
bibliography:
  # cruse.bib
  - bibliography.bib
  - cruse.bib
csl: apa.csl
editor:
  markdown:
    wrap: sentence
execute: 
  echo: false
  message: false
number-sections: true
latex-clean: false
pdf-engine: pdflatex
knitr:
  opts_chunk:
    fig.path: images/
format: 
  # html: default
  # docx: default
# # # # Uncomment for formatted version
  elsevier-pdf:
    linestretch: 2
    keep-tex: true
    journal:
      name: European Transport Research Review
      formatting: preprint
      model: 3p
      cite-style: super
# # # #   # pdf: default

>>>>

---
title: "Cycle Route Uptake and Scenario Estimation (CRUSE): an approach for developing strategic cycle network planning tools"
# subtitle: A case study of Ireland
bibliography:
  # cruse.bib
  - bibliography.bib
  - cruse.bib
csl: apa.csl
editor:
  markdown:
    wrap: sentence
execute: 
  echo: false
  message: false
number-sections: true
latex-clean: false
pdf-engine: pdflatex
knitr:
  opts_chunk:
    fig.path: images/
format: 
  # html: default
  # docx: default
# # # # Uncomment for formatted version
  elsevier-pdf:
    linestretch: 2
    keep-tex: true
    journal:
      name: European Transport Research Review
      formatting: preprint
      model: 3p
      cite-style: super
# # # #   # pdf: default

### 2024-03-24 paper.tex
Update title

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Cycle Route Uptake and Scenario Estimation (CRUSE): an open and nationally scalable approach for strategic cycle network planning tool development},
  pdfauthor={Robin Lovelace; Joey Talbot; Eugeni Vidal-Tortosa; Hussein Mahfouz; Elaine Brick; Peter Wright; Gary O'Tool; Dan Brennan; Suzanne Meade},
  pdfkeywords={Cycling, Open-source, Road Safety, Active Travel},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{Cycle Route Uptake and Scenario Estimation (CRUSE): an open and
nationally scalable approach for strategic cycle network planning tool
development \\\large{A case study of Ireland} }
\author[1]{Robin Lovelace%
\corref{cor1}%
}
 \ead{r.lovelace@leeds.ac.uk} 
\author[1]{Joey Talbot%
%
}

@@

\begin{abstract}
This paper describes an approach to the development of strategic cycle
network planning tools. Based on our experience developing and deploying
the Cycle Route Uptake and Scenario Estimation (CRUSE) Tool for Ireland,
we outline the methods used to generate the evidence presented in the
tool, including disaggregation of origin-destination data, additional
trip purposes, routing, scenarios of cycling potential, and the user
interface. The CRUSE Tool provides estimates of cycling currently and
under four scenarios of cycling potential: Near Market, Climate Action
Plan, Go Dutch, and Ebike. The tool was commissioned by Transport
Infrastructure Ireland and is publicly available at
\url{https://cruse.bike/}, enabling planners, engineers, and other
stakeholders to make more evidence-based decisions. CRUSE goes beyond
previous work by: modelling networks at high levels of geographic
resolution; simulating multiple trip purposes (social, shopping and
personal utility trips plus recreational and cycle touring trips), in
addition to using official data on trips to work and education
locations; provision of estimates of `quietness' (a proxy for
cyclability) at the route segment level; and its provision of three
network types: `Fastest', `Balanced' and `Quietest' to help plan both
arterial and residential cycle networks. Workshops and unstructure
interview is stakeholders show that the tool is already being used in
practice, to inform urban, inter-urban and rural network development.
The approach and methods for strategic cycle network development tools
outlined in this paper can be applied and built-on in other places to
support the generation of evidence needed to support ambitious cycling
policies and interventions internationally.
\end{abstract}

@@

Stakeholder consultation by TII emphasized the need for a strong,
national, systematic but locally-specific evidence base on cycle
networks in both urban and rural Ireland. The evidence base had to scale
nationally to support strategic alignment with national, regional and
local policies, but also be useful for local network planning. TII also
requires

@@

@@

\caption{\label{fig-dublin}Illustration of the density of route networks
generated by the CRUSE Tool for Dublin City and surroundings (top) and
rural County Mayo on the West coast of Ireland (botton). Source: CRUSE
Tool, available at \url{https://cruse.bike/}.}

@@

This paper aims to describe the design, features and potential use of
the CRUSE Tool. In Section~\ref{sec-methods}, we outline the methods
used to generate the evidence presented in the CRUSE Tool. In
Section~\ref{sec-results}, we present the results of the CRUSE Tool,
including estimates of current cycling levels and future cycling
potential at the national, regional and local levels. In
Section~\ref{sec-discussion}, we discuss the implications of the results
for policy and practice. In Section~\ref{sec-conclusions}, we conclude
the paper.

@@

@@

The aim of the paper was to describe the design, features and potential
use of the CRUSE Tool. As outlined in the previous section, the CRUSE
Tool provides evidence on current and potential future cycling levels
across Ireland down to the street level, with potential assigned to
`fastest', `balanced' and `quietest' route networks. This provision of
multiple scenarios of behavior change \emph{and} multiple scenarios of
investment, for example in cycling infrastructure next to major roads vs
quiet residential streets, is a key feature of the CRUSE Tool.

@@

>>>>

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Cycle Route Uptake and Scenario Estimation (CRUSE): an approach for developing strategic cycle network planning tools},
  pdfauthor={Robin Lovelace; Joey Talbot; Eugeni Vidal-Tortosa; Hussein Mahfouz; Elaine Brick; Peter Wright; Gary O'Tool; Dan Brennan; Suzanne Meade},
  pdfkeywords={Cycling, Open-source, Road Safety, Active Travel},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{Cycle Route Uptake and Scenario Estimation (CRUSE): an approach
for developing strategic cycle network planning tools}
\author[1]{Robin Lovelace%
\corref{cor1}%
}
 \ead{r.lovelace@leeds.ac.uk} 
\author[1]{Joey Talbot%
%
}

@@

\begin{abstract}
This paper describes an approach for developing strategic cycle network
planning tools. Based on our experience developing and deploying the
Cycle Route Uptake and Scenario Estimation (CRUSE) Tool for Ireland, we
outline the methods used to generate the evidence presented in the tool,
including disaggregation of origin-destination data, additional trip
purposes, routing, scenarios of cycling potential, and the user
interface. The CRUSE Tool provides estimates of cycling currently and
under four scenarios of cycling potential: Near Market, Climate Action
Plan, Go Dutch, and Ebike. The tool was commissioned by Transport
Infrastructure Ireland and is publicly available at
\url{https://cruse.bike/}, enabling planners, engineers, and other
stakeholders to make more evidence-based decisions. CRUSE goes beyond
previous work by: modelling networks at high levels of geographic
resolution; simulating multiple trip purposes (social, shopping and
personal utility trips plus recreational and cycle touring trips), in
addition to using official data on trips to work and education
locations; provision of estimates of `quietness' (a proxy for
cyclability) at the route segment level; and its provision of three
network types: `Fastest', `Balanced' and `Quietest' to help plan both
arterial and residential cycle networks. Workshops and unstructure
interview is stakeholders show that the tool is already being used in
practice, to inform urban, inter-urban and rural network development.
The approach and methods for strategic cycle network development tools
outlined in this paper can be applied and built-on in other places to
support the generation of evidence needed to support ambitious cycling
policies and interventions internationally.
\end{abstract}

@@

Stakeholder consultation by TII emphasized the need for a strong,
national, systematic but locally-specific evidence base on cycle
networks in both urban and rural Ireland. The evidence base had to scale
nationally to support strategic alignment with national, regional and
local policies, but also be useful for local network planning.

@@

\includegraphics{images/paste-10.png}

@@

\caption{\label{fig-landing}Illustration of the landing page of the
CRUSE Tool for Ireland.}

@@

This describes describe the design, features and potential use of an
approach to strategic cycle network planning that is open, scalable, and
evidence-based. We label the approach Cycle Route Uptake and Scenario
Estimation (CRUSE) and present a case study of its application in
Ireland, the results of which are publicly available at
\href{https://cruse.bike/}{cruse.bike} in the CRUSE Tool for Ireland,
the landing page of which is illustrated in Figure~\ref{fig-landing}. In
Section~\ref{sec-methods}, we outline the methods used to generate the
evidence presented in the CRUSE Tool. In Section~\ref{sec-results}, we
present the results of the CRUSE Tool, including estimates of current
cycling levels and future cycling potential at the national, regional
and local levels. In Section~\ref{sec-discussion}, we discuss
limitations and possible future improvements to the approach, and the
implications of the results for Ireland before making concluding remarks
in Section~\ref{sec-conclusions}.

@@

\caption{\label{fig-dublin}Illustration of the density of route networks
generated by the CRUSE Tool for Dublin City and surroundings (top) and
rural County Mayo on the West coast of Ireland (botton). Source: CRUSE
Tool, publicly available at \href{https://cruse.bike/}{cruse.bike}.}

@@

The aim of the paper was to describe the design, features and potential
use of the `CRUSE' approach and resulting tool. As outlined in the
previous section, the CRUSE Tool provides evidence on current and
potential future cycling levels across Ireland down to the street level,
with potential assigned to `fastest', `balanced' and `quietest' route
networks. This provision of multiple scenarios of behavior change
\emph{and} multiple scenarios of investment, for example in cycling
infrastructure next to major roads vs quiet residential streets, is a
key feature of the CRUSE Tool.

\subsection{Uses of the tool in
practice}\label{uses-of-the-tool-in-practice}

@@

\subsection{Comparison with other tools and contribution to the
field}\label{comparison-with-other-tools-and-contribution-to-the-field}
